A Standardized Effect Size for Evaluating and Comparing the Strength of Phylogenetic Signal

### 2020-08-25 Manuscript/PNAS-Adams-03-EKB.tex
03-MLC

\begin{figure}
\centering
\includegraphics[width=8.25cm]{fig.1.png}
\caption{Response of Pagel's \(\lambda\) to increasing strength of
Brownian motion. Gray line signifies the 1:1 line where the input value
matches the estimate \(\hat\lambda\). At each input level, the dark
black line represents the empirically derived expected value (mean) of
\(\hat\lambda\), the red line is the standard deviation of
\(\hat\lambda\), and the blue line is Shapiro Wilks statistic of
\(\hat\lambda\) (\(W=1.0\) signifies normality, \(W< 1.0\) represent
skewed distributions).{}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=8.25cm]{fig.2.png}
\caption{Response of Blomberg's \(\hat\kappa\) to increasing strength of Brownian motion. Gray line signifies the 1:1 line where the input value matches the estimate \(\hat\kappa\). At each input level, the dark black line represents the empirically derived expected value (mean) of
\(\hat\kappa\), the red line is the standard deviation of
\(\hat\kappa\), and the blue line is Shapiro Wilks statistic of
\(\hat\kappa\) (\(W=1.0\) signifies normality, \(W< 1.0\) represent
skewed distributions).{}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=8.25cm]{fig.3.png}
\caption{Response of effect sizes \(Z_{\lambda}\) and \(Z_K\) to increasing strength of Brownian motion.{}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{fig.4.png}
\caption{(A) Linear measures for relative body size, and regions of the
body used to estimate surface area to volume (SA:V) ratios. (B)
Permutation distributions of phylogenetic signal for SA:V and
\(\frac{BW}{SVL}\), with observed values shown as vertical bars. (C)
Effect sizes (\(Z_K\)) for SA:V and \(\frac{BW}{SVL}\), with their 95\%
confidence intervals (CI not standardized by \(\sqrt(n)\)).{}}
\end{figure}

@@

As an alternative, we described a standardized effect size (\(Z\)) for
assessing the strength of phylogenetic signal. \(Z\) expresses the
magnitude of phylogenetic signal as a standard normal deviate, which is
easily interpretable as the strength of phylogenetic signal relative to
the mean. We applied this concept to both \(\lambda\) and \emph{K}, and
found that \(Z_K\) was a better estimate of the strength of phylogenetic
signal in phenotypic data. First, values of \(Z_K\) more accurately
tracked known changes in the magnitude of phylogenetic signal, as
demonstrated by the near linear relationship between \(Z_K\) and input
signal. Additionally, the precision of \(Z_K\) was more consistent
across the range of input levels of phylogenetic signal. Thus, \(Z_K\)
is a more reliable measure of the relative strength of phylogenetic
signal, and places that effect on a common and comparable scale. We
therefore recommend that future studies interested in evaluating the
strength of phylogenetic signal incorporate \(Z_K\) as a statistical
measure of this effect.

@@

This study is not the first to compare \(\lambda\) and \emph{K} for
their ability as statistics to measure phylogenetic signal. Our results
for \(\lambda\) and \emph{K} values are consistent with those found in
the simulations performed by Münkemüller et al.~(18), but that study
investigated type I error rates and statistical power, finding that
\(\lambda\) performed better in both regards, irrespective of species
number in trees. Although not the central focus of their study, the same
tendency for variable \(\lambda\) and consistent \emph{K} at
intermediate phylogenetic signal strengths was observed (Fig. 2 of ref.
(18)). Recent work by Molina-Venegas and Rodríguez (21) found that
\emph{K} but not \(\lambda\) tended to inflate the estimate of
phylogenetic signal, leading to moderate type I and type II biases, if
polytomic chronograms were used. Their work more thoroughly addressed
previous observations of inflated \emph{K} for incompletely resolved
phylogenetic trees (18, 46). An interesting question is whether an
inflated \emph{K} value leads to an inflated \(Z_K\) or does a tendency
of a particular tree to inflate estimates of \emph{K} also inflate the
values in random permutations of a test, in which case \(Z_K\) is robust
to polytomies? We repeated the analyses in Figs. 1 \& 2, adjusting trees
to have 50\% collapsed nodes, per the technique of Molina-Venegas and
Rodríguez (21), and found results were consistent (Supporting
Information). This confirms that any tendency of incompletely resolved
trees to inflate \emph{K} as a descriptive statistic does not inflate
\(Z_K\) as an effect size. Furthermore, because comparison of effect
sizes in a test is a comparison of locations of observed values in their
sampling distributions, which would shift concomitantly because of this
tendency, the \(Z_{12}\) test statistic in equation 4 appears to be
robust in spite of unresolved trees.

@@

\textbf{Simulations.} Simulations were conducted by generating
pure-birth phylogenies at each of six different tree sizes
(\(n=2^5, 2^6, \cdots, 2^{10}\)), and with differing levels of
phylogenetic signal (\(\lambda=0.0, 0.5, \cdots, 1.0\)). We generated
100 random trees for each intersection of tree size and \(\lambda\). For
each \(\lambda\) within each tree size, continuous traits were then
simulated on each phylogeny under a BM model of evolution. For each set
of 100 trees we measured the mean values of \(\hat{\lambda}\) and
\emph{K}, their standard deviation, and calculated the Shapiro-Wilk
\(W\) statistic as a departure from normality (symmetry). For the
latter, a value of \(1.0\) indicates normally distributed values, while
departures from \(1.0\) indicate skewness. Simulations were then
repeated for both balanced and pectinate trees, which yielded
qualitatively similar results (see Supporting Information). Trees
containing polytomies, and an evaluation of \(\hat{\lambda}\) from
models of linear regression and phylogenetic ANOVA, were also
investigated, and results were qualitatively similar to those reported
above (see Supporting Information).

>>>>

\begin{figure}
\centering
\includegraphics[width=8.25cm]{{fig.1}.png}
\caption{Response of Pagel's \(\lambda\) to increasing strength of
Brownian motion. Gray line signifies the 1:1 line where the input value
matches the estimate \(\hat\lambda\). At each input level, the dark
black line represents the empirically derived expected value (mean) of
\(\hat\lambda\), the red line is the standard deviation of
\(\hat\lambda\), and the blue line is Shapiro Wilks statistic of
\(\hat\lambda\) (\(W=1.0\) signifies normality, \(W< 1.0\) represent
skewed distributions).{}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=8.25cm]{{fig.2}.png}
\caption{Response of Blomberg's *K* to increasing strength of Brownian motion. ~~Gray line signifies the 1:1 line where the input value matches the estimate \(\hat K\).~~ At each input level, the dark black line represents the empirically derived expected value (mean) of
*K*, the red line is the standard deviation of
*K*, and the blue line is Shapiro Wilks statistic of
*K* (\(W=1.0\) signifies normality, \(W< 1.0\) represent
skewed distributions).{}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=8.25cm]{{fig.3}.png}
\caption{Response of effect sizes \(Z_{\lambda}\) and \(Z_K\) to increasing strength of Brownian motion.{}}
\end{figure}

@@

{[}(A) Linear measures for relative body size, and regions of the body
used to estimate surface area to volume (SA:V) ratios. (B) Permutation
distributions of phylogenetic signal for SA:V and \(\frac{BW}{SVL}\),
with observed values shown as vertical bars. (C) Effect sizes (\(Z_K\))
for SA:V and \(\frac{BW}{SVL}\), with their 95\% confidence intervals
(CI not standardized by \(\sqrt(n)\)).{}{]}\{\{fig.4\}\}.png)

@@

As an alternative, we described a standardized effect size (\(Z\)) for
assessing the strength of phylogenetic signal. \(Z\) expresses the
magnitude of phylogenetic signal as a standard normal deviate, which is
easily interpretable as the strength of phylogenetic signal relative to
the mean. We applied this concept to both \(\lambda\) and \emph{K}, and
found that \(Z_K\) was a better estimate of the strength of phylogenetic
signal in phenotypic data. First, values of \(Z_K\) more accurately
tracked known changes in the magnitude of phylogenetic signal, as
demonstrated by the near linear relationship between \(Z_K\) and input
signal. Additionally, the precision of \(Z_K\) was more consistent
across the range of input levels of phylogenetic signal (Fig S1;
Supporting Information). Thus, \(Z_K\) is a more reliable measure of the
relative strength of phylogenetic signal, and places that effect on a
common and comparable scale. We therefore recommend that future studies
interested in evaluating the strength of phylogenetic signal incorporate
\(Z_K\) as a statistical measure of this effect.

@@

This study is not the first to compare \(\lambda\) and \emph{K} for
their ability as statistics to measure phylogenetic signal. Our results
for \(\lambda\) and \emph{K} values are consistent with those found in
the simulations performed by Münkemüller et al.~(18), but that study
investigated type I error rates and statistical power, finding that
\(\lambda\) performed better in both regards, irrespective of species
number in trees. Although not the central focus of their study, the same
tendency for variable \(\lambda\) and consistent \emph{K} at
intermediate phylogenetic signal strengths was observed (Fig. 2 of ref.
(18)). Recent work by Molina-Venegas and Rodríguez (21) found that
\emph{K} but not \(\lambda\) tended to inflate the estimate of
phylogenetic signal, leading to moderate type I and type II biases, if
polytomic chronograms were used. Their work more thoroughly addressed
previous observations of inflated \emph{K} for incompletely resolved
phylogenetic trees (18, 46). An interesting question is whether an
inflated \emph{K} value leads to an inflated \(Z_K\) or does a tendency
of a particular tree to inflate estimates of \emph{K} also inflate the
values in random permutations of a test, in which case \(Z_K\) is robust
to polytomies? We repeated the analyses in Figs. 1 \& 2, adjusting trees
to have 20\% collapsed nodes \sout{, per the technique of Molina-Venegas
and Rodríguez (21),} and found results were consistent (Supporting
Information). This confirms that any tendency of incompletely resolved
trees to inflate \emph{K} as a descriptive statistic does not inflate
\(Z_K\) as an effect size. Furthermore, because comparison of effect
sizes in a test is a comparison of locations of observed values in their
sampling distributions, which would shift concomitantly because of this
tendency, the \(Z_{12}\) test statistic in equation 4 appears to be
robust in spite of unresolved trees.

@@

\textbf{Simulations.} Simulations were conducted by generating
pure-birth phylogenies at each of six different tree sizes
(\(n=2^5, 2^6, \cdots, 2^{10}\)), and with differing levels of
phylogenetic signal (\(\lambda=0.0, 0.5, \cdots, 1.0\)). We generated 50
random trees for each intersection of tree size and \(\lambda\). For
each \(\lambda\) within each tree size, continuous traits were then
simulated on each phylogeny under a BM model of evolution. For each set
of 50 trees we measured the mean values of \(\hat{\lambda}\) and
\emph{K}, their standard deviation, and calculated the Shapiro-Wilk
\(W\) statistic as a departure from normality (symmetry). For the
latter, a value of \(1.0\) indicates normally distributed values, while
departures from \(1.0\) indicate skewness. Simulations were then
repeated for both balanced and pectinate trees, which yielded
qualitatively similar results (see Supporting Information). Trees
containing polytomies, and an evaluation of \(\hat{\lambda}\) from
models of linear regression and phylogenetic ANOVA, were also
investigated, and results were qualitatively similar to those reported
above (see Supporting Information).

### 2020-08-25 Manuscript/PNAS-Adams-03-MLC.Rmd
03-MLC

\begin{figure}
\centering
\includegraphics[width=8.25cm]{fig.1.png}
\caption{Response of Pagel's \(\lambda\) to increasing strength of
Brownian motion. Gray line signifies the 1:1 line where the input value
matches the estimate \(\hat\lambda\). At each input level, the dark
black line represents the empirically derived expected value (mean) of
\(\hat\lambda\), the red line is the standard deviation of
\(\hat\lambda\), and the blue line is Shapiro Wilks statistic of
\(\hat\lambda\) (\(W=1.0\) signifies normality, \(W< 1.0\) represent
skewed distributions).{}}
\end{figure}

**Lambda ($\lambda$) estimates of phylogenetic signal are inaccurate.** Computer simulations reveal that for $\hat{\lambda}$, the distributional expectations of a Bernoulli variable were mostly upheld. First, the mean value of $\hat{\lambda}$ increases as $\lambda$ increases, but it is negatively-biased (particularly for small tree sizes), and is consistently less than the input $\lambda$ value across most of its range (Fig. 1 black line). Second, the standard deviation of $\hat{\lambda}$ is largest at intermediate values of $\lambda$ and smallest at extreme values (Fig.1 red line), implying that the precision in estimating $\lambda$ varies across the range of input values. Additionally, standard deviations of $\hat{\lambda}$ are negatively associated with tree size, and for tress of 128 species or less, $\hat{\lambda}$ are quite variable, except for cases when $\lambda$ is near or equal to $1$. Third, the distributions of $\hat{\lambda}$ are not normal across its range, but become increasingly skewed at more extreme values of $\lambda$ (Fig. 1 blue line). For small tree sizes, it is also clear that distributions are more platykurtic at intermediate values of $\hat{\lambda}$. Taken together these results reveal that $\hat\lambda$ inconsistently estimates  phylogenetic signal, both across tree sizes and across the range of input values. Additional simulations (Supporting Information) reveal that incorporating $\hat\lambda$ in PGLS ANOVA and regression does not adversely affect the statistical properties of PGLS parameter estimation or model evaluation (type I error, power, bias in coefficients). Thus, it is reasonable to incorporate $\hat\lambda$ in PGLS as a parameter for tuning the degree of phylogenetic signal in the dependent variables during the analysis. However, the statistical properties shown in Fig. 1 demonstrate that $\lambda$ is unsuitable as an effect size for measuring the strength of phylogenetic signal in data, and thus $\lambda$ should not be used for comparing phylogenetic signal across datasets.

\begin{figure}
\centering
\includegraphics[width=8.25cm]{fig.2.png}
\caption{Response of Blomberg's *K* to increasing strength of Brownian motion. ~~Gray line signifies the 1:1 line where the input value matches the estimate \(\hat K\).~~ At each input level, the dark black line represents the empirically derived expected value (mean) of
*K*, the red line is the standard deviation of
*K*, and the blue line is Shapiro Wilks statistic of
*K* (\(W=1.0\) signifies normality, \(W< 1.0\) represent
skewed distributions).{}}
\end{figure}

**Kappa (*K*) estimates of phylogenetic signal are more reliable.** Simulation results demonstrate that *K* displays better statistical properties. First, as expected, mean values of *K* increase with increasing signal ($\lambda$) irrespective of tree size, albeit non-linearly (Fig. 2 black line). Additionally, the standard deviation of *K* is consistent across tree sizes (Fig. 2 red line), and while it increases with $\lambda$, it is always less than the mean. This finding is perhaps unsurprising, as *K* is lower-bounded by 0, and is never large for small values of $\lambda$. Importantly, *K* is normally distributed across the range of input $\lambda$; a consistent pattern regardless of tree size (Fig. 2 blue line). This result differs from those of [@Munkemuller_et_al2012], where the skewing appears to be the result of combining random values generated independently, rather than being a property of *K* itself. Overall, these findings reveal that while *K* is more reliable as an estimate of phylogenetic signal, the non-linear scaling with input signal implies that it should not be considered an effect size that measures the strength of phylogenetic signal on a common scale for comparison across datasets.

@@

where $\theta_{obs}$ is the observed test statistic, $E(\theta)$ is its expected value under the null hypothesis, and $\sigma_\theta$ is its standard error [@Glass1976; @Cohen1988;@Rosenthal1994]. Typically, $\theta_{obs}$ and $\sigma_\theta$ are estimated from the data, while $E(\theta)$ is obtained from the distribution of $\theta$ derived from parametric theory. However, recent advances in resampling theory [@Collyer_et_al2015a;@AdamsCollyer2016; @CollyerAdams2018;@AdamsCollyer2019b] have shown that $E(\theta)$ and $\sigma_\theta$ may also be obtained from an empirical sampling distribution of $\theta$ obtained from permutation procedures.

@@

where $K_{obs}$ is the observed phylogenetic signal, and $\hat\mu_K$ and $\hat\sigma_K$ are the mean and standard deviation of the empirical sampling distribution of *K* obtained via permutation. The empirical sampling distribution of *K* is first transformed via a Box-Cox transformation to better adhere to the assumption of normality.

@@

\begin{figure}
\centering
\includegraphics[width=8.25cm]{fig.3.png}
\caption{Response of effect sizes \(Z_{\lambda}\) and \(Z_K\) to increasing strength of Brownian motion.{}}
\end{figure}

@@

This study is not the first to compare $\lambda$ and *K* for their ability as statistics to measure phylogenetic signal.  Our results for $\lambda$ and *K* values are consistent with those found in the simulations performed by Münkemüller et al. [-@Munkemuller_et_al2012], but that study investigated type I error rates and statistical power, finding that $\lambda$ performed better in both regards, irrespective of species number in trees.  Although not the central focus of their study, the same tendency for variable $\lambda$ and consistent *K* at intermediate phylogenetic signal strengths was observed (Fig. 2 of ref. [@Munkemuller_et_al2012]). Recent work by Molina-Venegas and Rodríguez [-@MolinaVenegas2017] found that *K* but not $\lambda$ tended to inflate the estimate of phylogenetic signal, leading to moderate type I and type II biases, if polytomic chronograms were used.  Their work more thoroughly addressed previous observations of inflated *K* for incompletely resolved phylogenetic trees [@Davies2012; @Munkemuller_et_al2012].  An interesting question is whether an inflated *K* value leads to an inflated $Z_K$ or does a tendency of a particular tree to inflate estimates of *K* also inflate the values in random permutations of a test, in which case $Z_K$ is robust to polytomies?  We repeated the analyses in Figs. 1 & 2, adjusting trees to have 20% collapsed nodes ~~, per the technique of Molina-Venegas and Rodríguez [-@MolinaVenegas2017],~~ and found results were consistent (Supporting Information).  This confirms that any tendency of incompletely resolved trees to inflate *K* as a descriptive statistic does not inflate $Z_K$ as an effect size. Furthermore, because comparison of effect sizes in a test is a comparison of locations of observed values in their sampling distributions, which would shift concomitantly because of this tendency, the $Z_{12}$ test statistic in equation 4 appears to be robust in spite of unresolved trees.

>>>>

\begin{figure}
\centering
\includegraphics[width=8.25cm]{{fig.1}.png}
\caption{Response of Pagel's \(\lambda\) to increasing strength of
Brownian motion. Gray line signifies the 1:1 line where the input value
matches the estimate \(\hat\lambda\). At each input level, the dark
black line represents the empirically derived expected value (mean) of
\(\hat\lambda\), the red line is the standard deviation of
\(\hat\lambda\), and the blue line is Shapiro Wilks statistic of
\(\hat\lambda\) (\(W=1.0\) signifies normality, \(W< 1.0\) represent
skewed distributions).{}}
\end{figure}

**Lambda ($\lambda$) estimates of phylogenetic signal are inaccurate.** Computer simulations reveal that for $\hat{\lambda}$, the distributional expectations of a Bernoulli variable were mostly upheld. First, the mean value of $\hat{\lambda}$ increases as $\lambda$ increases.  Second, the standard deviation of $\hat{\lambda}$ is largest at intermediate values of $\lambda$ and smallest at extreme values (Fig.1 red line), implying that the precision in estimating $\lambda$ varies across the range of input values. Third, the distributions of $\hat{\lambda}$ tend toward normal ddistributions at intermediate levels of $\lambda$ but become increasingly skewed at more extreme values of $\lambda$ (Fig. 1 blue line). For small tree sizes, it is also clear that distributions are more platykurtic at intermediate values of $\hat{\lambda}$.  However, the mean value of $\hat{\lambda}$ is negatively-biased (particularly for small tree sizes but also consistently across most of its range; Fig. 1 black line) and standard deviations of $\hat{\lambda}$ are negatively associated with tree size.  For tress of 128 species or less, $\hat{\lambda}$ are quite variable, except for cases when $\lambda$ is near or equal to $1$. Taken together these results reveal that $\hat\lambda$ is a biased statistic that inconsistently estimates  phylogenetic signal, both across tree sizes and across the range of input values. Additional simulations (Supporting Information) reveal that incorporating $\hat\lambda$ in PGLS ANOVA and regression does not adversely affect the statistical properties of PGLS parameter estimation or model evaluation (type I error, power, bias in coefficients). Thus, it is reasonable to incorporate $\hat\lambda$ in PGLS as a parameter for tuning the degree of phylogenetic signal in the dependent variables during the analysis. However, the statistical properties shown in Fig. 1 demonstrate that $\lambda$ is unsuitable as an effect size for measuring the strength of phylogenetic signal in data, and thus $\lambda$ should not be used for comparing phylogenetic signal across datasets.

\begin{figure}
\centering
\includegraphics[width=8.25cm]{{fig.2}.png}
\caption{Response of Blomberg's *K* to increasing strength of Brownian motion.  At each input level, the black line represents the empirically derived expected value (mean) of
*K*, the red line is the standard deviation of
*K*, and the blue line is Shapiro Wilks statistic of
*K* (\(W=1.0\) signifies normality, \(W< 1.0\) represent
skewed distributions).{}}
\end{figure}

**Kappa (*K*) estimates of phylogenetic signal are more reliable.** Simulation results demonstrate that *K* displays better statistical properties. First, as expected, mean values of *K* increase with increasing signal ($\lambda$) irrespective of tree size, albeit non-linearly (Fig. 2 black line). Additionally, the standard deviation of *K* is consistent across tree sizes (Fig. 2 red line), and while it increases with $\lambda$, it is always less than the mean (low coefficient of variation). This finding is perhaps unsurprising, as *K* is lower-bounded by 0, and is never large for small values of $\lambda$. Importantly, *K* is normally distributed across the range of input $\lambda$; a consistent pattern regardless of tree size (Fig. 2 blue line). This result differs from those of [@Munkemuller_et_al2012], where the skewing appears to be the result of combining random values generated independently, rather than being a property of *K* itself. Overall, these findings reveal that while *K* is more reliable as an estimate of phylogenetic signal, the non-linear scaling with input signal implies that it should not be considered an effect size that measures the strength of phylogenetic signal on a common scale for comparison across datasets.

@@

where $\theta_{obs}$ is the observed test statistic, $E(\theta)$ is its expected value under the null hypothesis, and $\sigma_\theta$ is its standard error [@Glass1976; @Cohen1988;@Rosenthal1994]. Typically, $\theta_{obs}$ and $\sigma_\theta$ are estimated from the data, while $E(\theta)$ is obtained from the distribution of $\theta$ derived from parametric theory. However, recent advances in resampling theory [@Collyer_et_al2015a;@AdamsCollyer2016; @CollyerAdams2018;@AdamsCollyer2019b] have shown that $E(\theta)$ and $\sigma_\theta$ may also be obtained from an empirical sampling distribution of $\theta$ simulated from permutation procedures.

@@

where $K_{obs}$ is the observed phylogenetic signal, and $\hat\mu_K$ and $\hat\sigma_K$ are the mean and standard deviation of the empirical sampling distribution of *K* obtained via permutation. The empirical sampling distribution of *K* can be first transformed via a Box-Cox transformation to better adhere to the assumption of normality.

@@

\begin{figure}
\centering
\includegraphics[width=8.25cm]{{fig.3}.png}
\caption{Response of effect sizes \(Z_{\lambda}\) and \(Z_K\) to increasing strength of Brownian motion.  Means from simulation runs are shown for comparative ease. Individual values from each simulation run are available in Supporting Informaton. }
\end{figure}

@@

This study is not the first to compare $\lambda$ and *K* for their ability as statistics to measure phylogenetic signal.  Our results for $\lambda$ and *K* values are consistent with those found in the simulations performed by Münkemüller et al. [-@Munkemuller_et_al2012], but that study investigated type I error rates and statistical power, finding that $\lambda$ performed better in both regards, irrespective of species number in trees.  Although not the central focus of their study, the same tendency for variable $\lambda$ and consistent *K* at intermediate phylogenetic signal strengths was observed (Fig. 2 of ref. [@Munkemuller_et_al2012]). Recent work by Molina-Venegas and Rodríguez [-@MolinaVenegas2017] found that *K* but not $\lambda$ tended to inflate the estimate of phylogenetic signal, leading to moderate type I and type II biases, if polytomic chronograms were used.  Their work more thoroughly addressed previous observations of inflated *K* for incompletely resolved phylogenetic trees [@Davies2012; @Munkemuller_et_al2012].  An interesting question is whether an inflated *K* value leads to an inflated $Z_K$ or does a tendency of a particular tree to inflate estimates of *K* also inflate the values in random permutations of a test, in which case $Z_K$ is robust to polytomies?  We repeated the analyses in Figs. 1 & 2, adjusting trees to have 20% collapsed nodes, per the technique of Molina-Venegas and Rodríguez [-@MolinaVenegas2017], and found results were consistent (Supporting Information).  This confirms that any tendency of incompletely resolved trees to inflate *K* as a descriptive statistic does not inflate $Z_K$ as an effect size. Furthermore, because comparison of effect sizes in a test is a comparison of locations of observed values in their sampling distributions, which would shift concomitantly because of this tendency, the $Z_{12}$ test statistic in equation 4 appears to be robust in spite of unresolved trees.
